---
title: "Problem Set 2"
author: "Zoe Portlas"
date: "January 25, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Question 1
```{r}
r <- log(2)/109
log(10^12)/r
```
It would take about 4345 days and 2 hours for the cancer to reach a lethal number of cells.

### Question 2
$$\frac{dN}{dt} = b\frac{N}{N+M} -d$$

To find equilibrium points, set equal to zero and solve for N.

$$N = \frac{dM}{b-d}$$ or $$N = 0$$

To find stability, take the derivative of the original equation and set $N = \frac{dM}{b-d}$.

$$\frac{dF}{dN} = b \left (\frac{M}{(N+M)^{2}}\right )$$

##### Equilibrium point 1

$$\left. \frac{dF}{dN}\right|_{N=\frac{dM}{b-d}} = b \left (\frac{M}{(\left (\frac{dM}{b-d} \right )+M)^{2}}\right ) = \frac {(b-d)^{2}}{bM}$$

The equilibrium point is stable if $\frac {dF}{dN} < 0$.

$\left (b-d \right )^{2}$ is always greater than or equal to 0. When $b \neq d$ and $bM < 0$, the equilibrium point is stable, i.e. never because it is not possible to have a negative birth rate or a negative number of males.

##### Equilibrium point 2

$$\left. \frac{dF}{dN}\right|_{N=0} = b \left (\frac{M}{(0+M)^{2}}\right ) = \frac{b}{M}$$
Not stable because can't be <0?

Allee effect: Even if population is slightly higher than 0, the population won't be able to recover at a certain point because there were no suitable mates for the females.

### Question 3
```{r}
require(deSolve)
## Loading required package: deSolve
# Initial values
state <- c(N=10)
times <- seq(0,100,by=0.1)

# Parameters
parameters <- c(b = 2.4,c=0.02,M=50,d=0.2)

# Model
sterile_insect <- function(t,state,parameters){
  with(as.list(c(state,parameters)),{
       dN <- b*N/(N+M) - d - c*N
      list(c(dN))   
  })}

# Solve model and plot results
out <- ode(y = state,times=times,func=sterile_insect,parms=parameters)
par(mfrow=c(1,1))
plot(out[,1],out[,2],ylab='N',xlab='time',las=1)
```
```{r}
# Straight line at:
# N0 <- 0 # given eq. point
N1 <- 10
N2 <- 50

#parameters
b = 2.4
c=0.02
M=50
d=0.2

# coordinates
x <-c(0,10,50)
y <- c(0,0,0)
points <- cbind(x,y)

curve(b*x/(x+M)-d-c*x, from = -50, to = 100, xlab = "x", ylab = "y")
points(points)

# I couldn't figure out how to make the open and closed points
```